---
title: "DDP Week 3 Assignment"
author: "Joe M -- 27-DEC-2020"
output:
  html_document:
    df_print: paged
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
```

``` {r set_upLibs, message= FALSE}
library(plotly)
library(dplyr)
```

# Overvierw
This page will reflect the use of Plotly in an R Markdown page. This page will consist of a PDF created through  
R Markdown. The PDF contains a plotly graph showing COVID 19 information.

To facilitate this assignment the infomraiotn used will be garnered from information available from 21-Jan-2020 to 8-Dec-2020. 
The data set "COVID 19 Daily Updates" was acquired from Kaggle:  (https://www.kaggle.com/gpreda/coronavirus-2019ncov)

The data from that dataset has been cut down to reflect just the state of New York (USA). THe data being pulled is the  
number of confirmed cases and the number of deaths. THese numbers have been formatted to a running sum up to the give date.  
This information will be plotted o show the increase in one over the other.

Note: The code to recreate this page will be at the bottom of this page.
Note: The formatted CSV sheet will also be available in the GITHUB repository to make recreation easier.


## Review


``` {r get_Data}
setwd("C:/Users/Hermit/Desktop/Coursera Course/Data Science Specialization - JH/9) Developing Data Products/Week 3/DDP_Wk3_Assgn")
covid_csv <- read.csv(file = "covid-19-NY.csv", header = TRUE, sep = ",")
```

``` {r Set_DataFormat}
covid_csv$R_Date <- as.Date(covid_csv$R_Date , format = "%m/%d/%y")
```

``` {r get_DataReview}
#covid_csv <as.data.frame(covid_csv)
str(covid_csv)
head(covid_csv, 3)
tail(covid_csv, 3)
```
The data consists for 4 columns; State, Date, Confirmed_RS, and Death_RS. The state is always  'New York'. The date ranges from `2-MAR-2020` to `9-DEC-2020`.

``` {r set_Model }
fig <- plot_ly(covid_csv, x = ~R_Date, y = ~Confirmed_RS, name = 'Confirmed Case', type = 'scatter', mode = 'lines')
fig <- fig %>% add_trace(y = ~Deaths_RS, name = 'Confirmed Death', mode = 'lines') 
```


``` {r show_Model}
fig
```
## R Markdown Code
###Setup - Libraries
``` {r set_upLibs, echo = TRUE, eval = FALSE}
```
### Get Data
``` {r get_Data, echo = TRUE, eval = FALSE}
```
### Set Up Data
``` {r Set_DataFormat, echo = TRUE, eval = FALSE}
```
### Performing Data Review
``` {r get_DataReview, echo = TRUE, eval = FALSE}
```
### Set up Plot/Model
``` {r set_Model, echo = TRUE, eval = FALSE}
```
### Show Plot/Model
``` {r show_Model, echo = TRUE, eval = FALSE}
```


